---
title: "Using pochi with Seurat"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using pochi with Seurat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


``` {r setup, echo = FALSE}
knitr::opts_chunk$set(tidy = FALSE,
                      dpi = 72,
                      fig.width = 9,
                      fig.height = 6,
                      width=80,
                      cache = FALSE,
                      dev = "png",
                      message = TRUE,
                      error = TRUE,
                      warning = TRUE)
```

# Introduction

## Installation
Currently, [pochi](http://github.com/diegoalexespi/pochi) is available at Github and can be downloaded using the devtools (or remotes) package.
```{r installation, eval = FALSE}
devtools::install_github("diegoalexespi/pochi")
```


# Loading data

## Loading required packages

The [pochi](http://github.com/diegoalexespi/pochi) package operates on [Seurat](http://github.com/satijalab/Seurat) objects. We load the `Seurat`, `SeuratData`, and `pochi` packages here for our analyses, as well as the `magrittr` package in order to improve legibility of code through using the pipe `%>%` operator.

```{r load packages required, eval = TRUE, warning=FALSE, message=FALSE}
require("Seurat")
require("SeuratData")
require("pochi")
require("ggplot2")
require("tidyr")
```

We load the pbmc3k data from the `SeuratData` package.
```{r loading pbmc3k data, eval = TRUE, warning=FALSE}
InstallData("pbmc3k")
pbmc3k_seurat <- LoadData("pbmc3k")
set.seed(789)
pbmc3k_seurat <- pbmc3k_seurat[,!is.na(pbmc3k_seurat$seurat_annotations)]
pbmc3k_seurat <- NormalizeData(pbmc3k_seurat)
pbmc3k_seurat$condition <- sample(c("WT", "KO"), size = ncol(pbmc3k_seurat), replace = TRUE)
pbmc3k_seurat$replicate <- sample(1:3, size = ncol(pbmc3k_seurat), replace = TRUE)
pbmc3k_seurat@meta.data %>% head()
```

# Visualizations

## `AbundancePlot`

```{r AbundancePlot, eval=TRUE, fig.width = 9, fig.height=8}
AbundancePlot(pbmc3k_seurat, group.by = "seurat_annotations", split.by = "condition", replicate.by = "replicate")
AbundancePlot(pbmc3k_seurat, group.by = "seurat_annotations", split.by = "condition", replicate.by = "replicate", paired = TRUE, draw_paths = TRUE, sina_shift = FALSE)
```

## `AssignQuantiles`

```{r AssignQuantiles, eval = TRUE}
pbmc3k_seurat <- AssignQuantiles(pbmc3k_seurat, feature = "B2M", assay = "RNA", slot = "data", split.by = "condition", quantile.probs = c(0,0.4,0.8,1))
RidgePlot(pbmc3k_seurat, group.by = "B2M.quantile", features = "B2M")
```

## `BackGatePlot`

```{r backgateplot, eval = TRUE}
BackgatePlot(pbmc3k_seurat, feature1 = "CD4", feature2 = "CD8A", metadata.col = "seurat_annotations", metadata.selection = "Memory CD4 T")
BackgatePlot(pbmc3k_seurat, feature1 = "CD4", feature2 = "CD8A", metadata.col = "seurat_annotations", metadata.selection = "CD8 T")
```

## `Heatmaps`

```{r heatmaps, eval = TRUE}
rna_markers <- presto::wilcoxauc(pbmc3k_seurat, group_by = "seurat_annotations")
top_rna_markers <- rna_markers %>% 
    dplyr::filter(padj < 0.01, logFC > 0) %>%
    dplyr::group_by(group) %>% 
    dplyr::slice_min(padj, with_ties = FALSE, n = 3)
DoStarHeatmap(pbmc3k_seurat, diff_exp_results = rna_markers %>% dplyr::filter(group != "Platelet"), assay = "RNA", slot = "data", group.by = "seurat_annotations", p_val_choice = 0.01, logFC_choice = 2)
DoClusteredHeatmap(pbmc3k_seurat, features = top_rna_markers$feature, assay = "RNA", group.by = "seurat_annotations")
```

## `MetaDataPlot`

```{r metadataplot, eval = TRUE}
MetaDataPlot(pbmc3k_seurat, group.by = "seurat_annotations", split.by = "replicate")
```

## `ModulePlot`

```{r moduleplot, eval = TRUE}
pbmc3k_seurat <- CellCycleScoring(pbmc3k_seurat, s.features = cc.genes.updated.2019$s.genes, g2m.features = cc.genes.updated.2019$g2m.genes)
ModulePlot(pbmc3k_seurat, features = "S.Score", assay = "RNA", split.by = "condition", replicate.by = "replicate")
```

## `VlnPlot.median`

```{r VlnPlot.median, eval = TRUE}
VlnPlot.median(pbmc3k_seurat, features = c("CD14","CD1c"))
```

## `QC.n.mad`

```{r QC.n.mad, eval = TRUE}
pbmc3k_seurat = QC.n.mad(pbmc3k_seurat)
```

## `Calc.Perc.Features`

```{r Calc.Perc.Features, eval = TRUE}
pbmc3k_seurat = Calc.Perc.Features(pbmc3k_seurat)
```

# Session Info
```{r session info, eval=TRUE, width=6}
sessionInfo()
```
